### 2020-11-02 thesis/thesis.tex
comment three, change wording
comment 4. added precisions

Connectivity modelling methods depend on the level of organization (individual, population, species or community) and the spatial scale (patch or  landscape) that connectivity is considered. To cover them all is beyond the scope of this introduction, but it is important to replace our choice of methodology in the larger body of foundational work on spatial ecological modelling. This thesis focuses on species level modelling at the landscape scale, and this focus has to be justified. Important efforts in the field of spatial ecological modelling relied on metapopulation theory, island biogeography (IBT), and population genetics. These bodies of theory spurred different approaches to modelling. For example, an IBT approach is focused on predicting diversity (number of species) in island patches \citep{macarthur_theory_1967} and has largely influenced other bodies of work in spatial ecology \citep{warren_how_2020}. On the other hand, metapopulation theory is focused on predicting long-term patch occupancy \citep{hanski_habitat_1999, hanski_metapopulation_2000}. Finally, population genetics focuses on predicting gene variation and flow within populations \citep{lewontin_population_1985, charlesworth_population_2017}. Unlike these methods, our goal is to estimate potential animal movement at the species level, over a large spatial and temporal extent. We therefore rely on a more appropriate approach which combines habitat suitability analysis and circuit theory modelling.\\

\cite{fletcher_spatial_2018} emphasizes three common approaches to connectivity modelling: structural landscape modelling, resistance-based modelling and graph-based measures. Structural models are simple representations of physical landscape barriers. Resistance based approaches can go beyond structural approaches by abstracting the landscape into a resistance surface representing the level of hindrance to animal movement into the landscape. The parameterization of resistance surfaces depends on the life history and ecology of a species, making it an appealing method for functional connectivity modeling.  This is the method used in this thesis: we derive resistance surfaces for multiple species as input to a habitat suitability analysis. Graph based approaches depend on graph theory and are also common and often seen as complementary to resistance-based approaches. \\

>>>>

Connectivity modelling methods depend on the level of organization (individual, population, species or community) and the spatial scale (patch or  landscape) that connectivity is considered. To cover them all is beyond the scope of this introduction, but it is important to replace our choice of methodology in the larger body of foundational work on spatial ecological modelling. This thesis focuses on species level modelling at the landscape scale, and this focus has to be justified. Important efforts in the field of spatial ecological modelling relied on metapopulation theory, island biogeography (IBT), and population genetics. These bodies of theory spurred different approaches to modelling. For example, an IBT approach is focused on predicting diversity (number of species) in island patches \citep{macarthur_theory_1967} and has largely influenced other bodies of work in spatial ecology \citep{warren_how_2020}. On the other hand, metapopulation theory is focused on predicting long-term patch occupancy \citep{hanski_habitat_1999, hanski_metapopulation_2000}. Finally, population genetics focuses on predicting gene variation and flow within populations \citep{lewontin_population_1985, charlesworth_population_2017}. Unlike these methods, our goal is to estimate potential animal movement at the species level, over a large spatial and temporal extent. We therefore rely on a different approach which combines habitat suitability analysis and circuit theory modelling.\\

\cite{fletcher_spatial_2018} emphasizes three common approaches to connectivity modelling: structural landscape modelling, resistance-based modelling and graph-based measures. Structural models are simple representations of physical landscape barriers. Resistance based approaches can go beyond structural approaches by abstracting the landscape into a resistance surface representing the level of hindrance to animal movement into the landscape. The parameterization of resistance surfaces depends on the life history and ecology of a species, making it an appealing method for functional connectivity modeling.  This is the method used in this thesis: we derive resistance surfaces for multiple species as input to a habitat suitability analysis. Graph based approaches are derived from graph theory (i.e. the study of networks of connected objects) and are also common and often seen as complementary to resistance-based approaches. \\
